---
title: "AAPI Interest Survey Analysis"
author: "Jemma"
date: "March 13, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm reading the data~ ^^
```{r}
data <- read.csv("/Users/cindella/Google Drive/AAPIData.csv")
data[1]
```

Re-labelling columns~~ ><
```{r}
think <- data[2]
#How often do you think about AAPI issues?
bffdiscuss <- data[3]
#How often to you discuss AAPI issues with your friends?
knowledge <- data[4]
#Rate how knowledgeable you are on AAPI issues
issueinterest <- data[5]
#What AAPI issues interest you?
freq_petition <- data[6]
#Please rate how frequently you do the following: [Signing a Paper Petition on an AAPI-related Issue]
freq_meeting <- data[7]
#Please rate how frequently you do the following: [Attending a meeting on AAPI-related issue]
freq_event <- data[8]
#Please rate how frequently you do the following: [Attending a rally or speech on AAPI-related issues]
freq_gov <- data[9]
#Please rate how frequently you do the following: [Contacting a government official regarding AAPI-related issues]
freq_volunteer <- data[10]
#Please rate how frequently you do the following: [Working or volunteering for AAPI-related causes]
freq_group <- data[11]
#Please rate how frequently you do the following: [Be an active member of a group that advocates for AAPI-related changes in policies]
socialmedia <- data[12]
#Do you use social media to engage in AAPI Issues?
engage_like <- data[13]
#If so, HOW often do you engage in AAPI issues? [Like or promote material related to AAPI issues]
engage_vote <- data[14]
#If so, HOW often do you engage in AAPI issues? [Encourage others to vote on a AAPI social/politcal issue]
engage_post <- data[15]
#If so, HOW often do you engage in AAPI issues? [Post your own thoughts/comments on AAPI issues]
engage_repost <- data[16]
#If so, HOW often do you engage in AAPI issues? [Repost content related to AAPI issues]
engage_action <- data[17]
#If so, HOW often do you engage in AAPI issues? [Encourage others to take action on AAPI issues that are important to you]
engage_link <- data[18]
#If so, HOW often do you engage in AAPI issues? [Post links to political stories/articles for others to read]
engage_group <- data[19]
#If so, HOW often do you engage in AAPI issues? [Belong to a group that is related to AAPI political/social issues or working to advance a cause]
engage_follow <- data[20]
#If so, HOW often do you engage in AAPI issues? [Follow elected officials, candidates for office and/or other public figures]
age <- data[21]
#Age
gender <- data[22]
#Gender
student <- data[22]
#Are you currently a student?
```

Creating composite scores
```{r}
data$AAPIinvolve <- (freq_petition + freq_meeting + freq_meeting + freq_event + freq_gov + freq_volunteer + freq_group)/6
data$socialmedia <- (engage_like + engage_post + engage_vote + engage_follow + engage_action + engage_repost + engage_group + engage_link)/8
summary(data$AAPIinvolve)
```


CORRELATION~~~~~~~~~
for t test: #1st_var = 2nd_estimate_std_value x (2nd_var) + intercept_estimate_std


~Involvement and social media engagement
```{r}
linear <- lm(as.matrix(AAPIinvolve) ~ as.matrix(socialmedia), data, na.action = na.exclude)
summary(linear)
#AAPIinvolve=1.0489(socialmedia)-0.4620 ***
```

~Thinking and knowledge 
```{r}
linear <- lm(as.matrix(knowledge) ~ as.matrix(think), data, na.action = na.exclude)
summary(linear)
#knowledge=0.8067(think)+0.2133 ***
```

~Talking with friends and thinking about issues
```{r}
linear <- lm(as.matrix(think) ~ as.matrix(bff.discuss), data, na.action = na.exclude)
summary(linear)
#think=0.6884(bff.discuss)+1.8961 ***
```

~Talking with friends and social media engagement
```{r}
linear <- lm(as.matrix(bff.discuss) ~ as.matrix(socialmedia), data, na.action = na.exclude)
summary(linear)
#bff.discuss=0.5570(socialmedia)+2.0897 *
```

Involvement and age 
```{r}
linear <- lm(as.matrix(AAPIinvolve) ~ as.matrix(age), data, na.action = na.exclude)
summary(linear)
#not significant
```

Involvement and gender 
```{r}
linear <- aov(as.matrix(AAPIinvolve) ~ as.matrix(gender), data, na.action = na.exclude)
summary(linear)
#not significant 
```

Social media and age
```{r}
linear <- lm(as.matrix(age) ~ as.matrix(socialmedia), data, na.action = na.exclude)
summary(linear)
#age=0.7275(socialmedia)+16.9424 *
```

Talking wth friends and knowledge
```{r}
linear <- lm(as.matrix(bff.discuss) ~ as.matrix(knowledge), data, na.action = na.exclude)
summary(linear)
#bff.discuss=0.4326(knowledge)+2.0411 **
```

Talking with friends and age
```{r}
linear <- lm(as.matrix(bff.discuss) ~ as.matrix(age), data, na.action = na.exclude)
summary(linear)
#not siginificant
```

```{r}
summary(as.matrix(age))
summary(as.matrix(bff.discuss))
summary(as.matrix(knowledge))
summary(as.matrix(socialmedia))
summary(as.matrix(think))
```
